\textbf{EECS 340: Assignment 3}

### 2020-02-21 assignment_3/article.tex
✨ Add ref in Q4(a) about Python implementation of quick_miss on Gists.
🐛 Fix Q2(a) incorrect substitution on T((1 − α)(k + 1)) in equation 3.

\begin{align}
    T(k + 1) &= T(\alpha(k + 1)) + T((1-\alpha)(k+1)) + d(k + 1) \\
    &\leq [c \cdot \alpha (k + 1) \log(\alpha(k + 1)) - c'(k+1)] + \nonumber\\
    & \ \ \ \ [c \cdot ((1- \alpha)(k + 1))\log((1-\alpha)(k + 1)) - c'(k+1)]+ d(k + 1) \nonumber \\
    &\leq c \cdot \alpha (k + 1) \log(\alpha(k + 1)) + c(1-\alpha)(k + 1)\log(\alpha(k+1)) + d(k + 1) - 2c'(k+1) \nonumber \\
    &\leq (c \alpha + c(k + 1) -  c \alpha) \cdot \log(\alpha(k + 1)) +  d(k + 1) - 2c'(k+1)\nonumber \\
    &\leq c(k + 1) \cdot \log(\alpha(k + 1)) +  (d-2c')(k + 1)\nonumber \\
    &\leq c(k + 1) \cdot \log(k + 1)+  (d-2c')(k + 1)\nonumber \\
    \Longrightarrow T(k + 1) &\leq c(k + 1) \cdot \log(k + 1) \ \ \ \text{for $c'= \frac{1}{2}d$}
\end{align}

As now we have $T(k + 1) \leq c(k + 1) \cdot \log(k + 1)$ for $c'= \frac{1}{2}d$, we may say it is true for $T(k)$ for all $k \in [1, n)$.
\end{proof}

@@

>>>>

\begin{align}
    T(k + 1) &= T(\alpha(k + 1)) + T((1-\alpha)(k+1)) + d(k + 1) \\
    &\leq [c \cdot \alpha (k + 1) \log(\alpha(k + 1)) - c'(k+1)] + \nonumber\\
    & \ \ \ \ [c \cdot ((1- \alpha)(k + 1))\log((1-\alpha)(k + 1)) - c'(1-\alpha)(k + 1)]+ d(k + 1) \nonumber \\
    &\leq c \cdot \alpha (k + 1) \log(\alpha(k + 1)) + c(1-\alpha)(k + 1)\log(\alpha(k+1)) +\nonumber \\
    & \ \ \ \  d(k + 1) - c'(k+1)- c'(1-\alpha)(k + 1) \nonumber \\
    &\leq (c \alpha + c(k + 1) -  c \alpha) \cdot \log(\alpha(k + 1)) +  d(k + 1) -  c'(1-\alpha + 1)(k + 1)\nonumber \\
    &\leq c(k + 1) \cdot \log(\alpha(k + 1)) +  (d-c'\alpha)(k + 1)\nonumber \\
    &\leq c(k + 1) \cdot \log(k + 1)+  (d-c'\alpha)(k + 1)\nonumber \\
    \Longrightarrow T(k + 1) &\leq c(k + 1) \cdot \log(k + 1) \ \ \ \text{for $c'= \frac{d}{\alpha}$}
\end{align}

As now we have $T(k + 1) \leq c(k + 1) \cdot \log(k + 1)$ for $c'= \frac{d}{\alpha}$, we may say it is true for $T(k)$ for all $k \in [1, n)$.
\end{proof}

@@

We also provide a runnable \ilc{Python} implenetation of the pseudo-code with real-time outputs. Please checkout
\href{https://gist.github.com/choH/aa6ef8d549216ca1aa47a2aedab8dfa8}{\ilc{quick\_miss.py}} if needed.
